### 2021-01-25 README.Rmd
transition predict to output vector

# Get predicted dbh values values
predictions <- comp_bayes_lm_ex %>%
  predict(focal_vs_comp = focal_vs_comp_ex) %>%
  right_join(ex_growth_df, by = c("focal_ID" = "ID"))

>>>>

# Get predicted dbh values values
predictions <- focal_vs_comp_ex %>%
  mutate(growth_hat = predict(comp_bayes_lm_ex, focal_vs_comp_ex))
